UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-15 main.tex
:pencil: Update UniScatter receiver

	However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are mixed by multiplication instead of superposition.

@@

	\emph{First,} we propose UniScatter node to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive channel coding at backscatter sources can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission.

	\emph{Second,} we propose a practical receiving strategy that semi-coherently decodes all UniScatter messages from the received energy during each backscatter symbol block, re-encodes and recovers their reflection patterns at each primary block, combines those with relevant \gls{csi} to construct equivalent primary channels, then coherently decodes the primary link under adapted multipath.
	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the difference of symbol period in backscatter decoding; 4) exploits the reflection patterns in primary decoding; 5) suits for diverse symbol period ratios.

@@

		% Next, we will discuss the input design in a UniScatter-enabled network.

@@

	\begin{subsection}{UniScatter Receiver}
		TODO
	\end{subsection}

	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A UniScatter-enabled single-user multi-node network.}
			\label{fi:uniscatter_network}
		\end{figure}
		% As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
		% UniScatter-enabled single-user multi-node \gls{miso} network where multiple UniScatter nodes ride over a point-to-point transmission to
		As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node \gls{miso} network where two coexisting systems share spectrum, energy and infrastructures.
		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna UniScatters.
		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna UniScatter nodes.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}
		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.

@@

		\begin{remark}
			UniScatter involves a symbiotic \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
			For each node, the reflection coefficient not only encodes the backscatter message, but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
			% As such, novel receiving strategy other than \gls{sic} should be tailored to signal characteristics to unveil how reflection pattern potentially influences the primary-backscatter tradeoff.
			To accommodate such signal characteristics, novel receiving strategy apart from \gls{sic} is desired to better utilize the reflection pattern and boost the primary-backscatter tradeoff.
		\end{remark}
	\end{subsection}

	\begin{subsection}{Receiving Strategy}
		We propose a UniScatter receiver where the backscatter messages of all UniScatter nodes are first jointly and semi-coherently detected using total received energy per backscatter block, then modeled within equivalent channel \eqref{eq:equivalent_channel} as dynamic passive beamforming.
		% identified by non-coherent energy detection, then
		% Compared with conventional schemes as joint decoding and \gls{sic}, the UniScatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
		% Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.
		Compared with \gls{ml} and \gls{sic}, UniScatter receiver allows practical and low-complexity node multiple access with minor adjustment over legacy equipments.

@@

		To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all UniScatter nodes over accumulated energy $z$.
		% To reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/energy_distribution.tex}
			% \caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
				\gls{pdf} of total received energy per backscatter block, conditioned on different input hypothesis.
				% This \gls{ml} decision consists of convex regions and is generally rate-suboptimal except for equiprobable inputs.}
				Here, the convex \gls{ml} decision regions are generally rate-suboptimal except for equiprobable inputs.
			\label{fi:energy_distribution}

@@

@@

\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold Design}
	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter-enabled network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		% \addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k,m_k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
	\end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	\addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\boldsymbol{p}_k \in \Delta^{M-1},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	% \addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	Problem \eqref{op:weighted_sum_rate} is highly non-convex, and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

@@

\begin{section}{Simulation Results}
	% TODO add distribution to initializer to smooth curves?
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node UniScatter-enabled network.
	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ UniScatter nodes are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
	% The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
	All nodes have amplitude scattering ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=4$ input states.
	% and we consider amplitude scattering ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \qty{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\qty{70}{\dBm}$ and receive antenna gain \qty{3}{\dBi}.
	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
	The parameters remain fixed unless otherwise specified.

>>>>

	However, the advantage of \gls{sic} is questionable because 1) sufficiently large symbol period ratio is assumed in primary rate analysis and constraints backscatter rate; 2) backscatter pattern and signal characteristics are not fully exploited; 3) non-coherent primary encoding is required at the transmitter, while re-encoding, precoding, and subtraction are required at the receiver; 4) primary and backscatter symbols are superimposed by multiplication instead of superposition.

@@

	\emph{First,} we propose UniScatter nodes to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive channel coding at backscatter sources can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission.

	% \emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes and recovers their reflection patterns, combines with relevant \gls{csi} for equivalent primary channel as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
	\emph{Second,} we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes for their reflection patterns, combines with relevant \gls{csi} as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the link difference and suits for diverse symbol period ratios; 4) requires minor modification over legacy hardware.

@@

		% Next, we will discuss the input design in a UniScatter network.

@@

	\begin{subsection}{UniScatter Receiver}
		Since each passive UniScatter node directly modulates its own message over the legacy signal, it involves a \emph{double modulation} where the primary and backscatter symbols are superimposed by \emph{multiplication coding} instead of superposition coding.
		Besides, the backscatter symbol period is typically longer than primary due to the load switching constraint.
		% ? In such case, the advantages of power-domain \gls{noma} with \gls{sic} receiver becomes questionable.
		% Those facts imply if the backscatter messages can be decoded first, one can recover the reflection patterns of all UniScatters and model them within the equivalent primary channel as if dynamic passive beamforming.
		Both facts imply backscatter detection under primary uncertainty is also part of equivalent primary channel training.
		Hence, we propose a practical UniScatter receiver that semi-coherently decodes UniScatter nodes from the received energy during each backscatter symbol block, re-encodes for their reflection patterns, combines with relevant \gls{csi} as if dynamic passive beamforming, then coherently decodes the primary link under the enhanced multipath.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of total received energy per backscatter block, conditioned on different input state hypotheses.
				$t$ and $\mathcal{R}$ denote the energy decision thresholds and regions, respectively.
			}
			\label{fi:energy_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:energy_distribution}, the total received energy during each backscatter symbol block is a random variable that follows different distributions conditioned on different input state hypotheses.
		Compared with conventional joint \gls{ml} and \gls{sic} from stronger primary link to weaker backscatter links, UniScatter receiver not only preserves the benefits of backscatter modulation and passive beamforming, but also enjoys much lower computational and operational complexities.
	\end{subsection}

	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A single-user multi-node UniScatter network.}
			\label{fi:uniscatter_network}
		\end{figure}
		In this subsection, we consider a single-user multi-node \gls{miso} UniScatter network as shown in Fig. \ref{fi:uniscatter_network}.
		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna UniScatters.
		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna UniScatter nodes.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}
		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.

@@

@@

		% !
		% To accommodate backscatter characteristics and reduce decoding complexity, we consider a joint semi-coherent detection for all UniScatter nodes over accumulated energy $z$.
		% % To reduce decoding complexity, we consider a joint semi-coherent energy detection for all UniScatters based on disjoint decision regions over accumulated energy $z$.
		% \begin{figure}[!t]
		% 	\centering
		% 	\resizebox{0.9\columnwidth}{!}{
		% 		\input{assets/illustration/energy_distribution.tex}
		% 	}
		% 	% \caption{\gls{pdf} of Average Received Power Conditioned on Different Input Hypothesis. Example \gls{ml}.}
		% 	\caption{
		% 		\gls{pdf} of total received energy per backscatter block, conditioned on different input hypothesis.
		% 		% This \gls{ml} decision consists of convex regions and is generally rate-suboptimal except for equiprobable inputs.}
		% 		Here, the convex \gls{ml} decision regions are generally rate-suboptimal except for equiprobable inputs.
		% 	}
		% 	\label{fi:energy_distribution}
		% \end{figure}

@@

		% !

@@

\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold Design}
	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		% \addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k,m_k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
	\end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	\addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\boldsymbol{p}_k \in \Delta^{M-1},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	% \addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	Problem \eqref{op:weighted_sum_rate} is highly non-convex, and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

@@

\begin{section}{Simulation Results}
	% TODO add distribution to initializer to smooth curves?
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input, beamforming and decision design over a single-user multi-node UniScatter network.
	We assume the distance between \gls{ap} and user is \qty{10}{\meter}, and $K=2$ UniScatter nodes are uniformly dropped within a disk centered at the user of radius \qty{1}{\meter}.
	% The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading for all channels.
	The carrier frequency is $f=\qty{200}{\MHz}$, and we consider \gls{iid} Ricean fading between all terminals.
	For direct, forward and backward links, we set the path loss exponents to \num{2.6}, \num{2.4} and \num{2}, and the Ricean factor to \num{5}, \num{5} and \num{10}, respectively.
	% For direct, forward and backward links, we choose path loss exponents \num{2.6}, \num{2.4} and \num{2}, and Ricean factor \num{5}, \num{5} and \num{10}, respectively.
	% and the path loss exponents for direct, forward and backward links are \num{2.6}, \num{2.4} and \num{2}, respectively.
	% We consider \gls{iid} Ricean fading for all channels with Ricean factor set to \num{5}, \num{5} and \num{10}
	The \gls{ap} has $Q=4$ antennas with maximum average transmit power $P=\qty{36}{\dBm}$.
	All nodes have amplitude scattering ratio $\alpha=0.5$, symbol period ratio $N=20$, and perform \gls{qam} with $M=4$ input states.
	% and we consider amplitude scattering ratio $\alpha=0.5$ and symbol period ratio $N=20$.
	% The user has a receive antenna gain of \qty{3}{\dBi} and average noise power
	The user is with average noise power $\sigma_v^2=\qty{70}{\dBm}$ and receive antenna gain \qty{3}{\dBi}.
	All rate regions are averaged over at least \num{1000} instances, where ``PSP'' and ``BSP'' means primary and backscatter symbol periods, respectively.
	We choose decision design by \gls{smawk} \cite{He2021} as reference, and select discretize boundaries uniformly over the \qty{95}{\percent} confidence region of edge hypotheses.
	The parameters remain fixed unless otherwise specified.
